%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV for A4 paper format
% XeLaTeX Template
% Version 1.0
%
% A4 version author:
% Marvin Frommhold (depressiverobot.com)
% https://github.com/depressiveRobot/friggeri-cv-a4
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Options
% 'print': remove colors from this template for printing
% 'nocolors' to disable colors in section headers
\documentclass[]{friggeri-cv}

% \addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{andrew}{alexander}{andrew@homeemail.me.uk} % Your name and current job title/field

%----------------------------------------------------------------------------------------
% SIDEBAR SECTION
%----------------------------------------------------------------------------------------
\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Oak Dell
Firs Drive, St Albans
Herts. AL4 8LB
United Kingdom
~
+44 7710 168 232
~
%\href{mailto:andrew@homeemail.me.uk}{\emailsymbol andrew@homeemail.me.uk}
\href{https://www.linkedin.com/in/andyalexanderuk}{\faLinkedinSign {} andyalexanderuk}
\href{https://github.com/andyalexander}{\faGithub {} andyalexander}
\section{programming}
Python, R
Javascript, SQL \& Java
pandas, sklearn    
\end{aside}


%----------------------------------------------------------------------------------------
% OVERVIEW
%----------------------------------------------------------------------------------------

\section{introduction}

I am someone who is motivated by using technology and advanced analytics to improve how decisions are made, and how this drives value.  I have a strong hands-on background in applying these approaches, most recently within a data science team for a leading investment bank, and prior to that as the analytics technology and data science CIO for a leading commodities trading house.

Having crossed between commercial and technology roles I appreciate the motivation and tensions that inevitably exist.  Throughout my career I have remained a ‘hands on’ leader / practitioner - recognising the importance of being able to 'lead from the front', as well as develop and implement longer term, and more strategic change.

I bring a unique blend of experience and skills covering hands on analytic roles, through technology strategy, full stack development, IT architecture and CIO responsibilities.  This enables me to as easily take the lead in a machine learning development project, as work a set of strategic options with C level executives or lead a development team.


%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2003--08}
{BSc {\normalfont Mathematics and Computer Science}}
{The Open University (part time)}
{First class honours (1:1)}

%------------------------------------------------

\entry
{1994--97}
{BSc {\normalfont Economics \& Accounting}}
{The University of Bristol}
{Second class honours (first division -- 2:1)}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

%\subsection{Full Time}

\begin{entrylist}

%------------------------------------------------

\entry
{2007--17}
{BP Plc - trading technology roles}
{London, UK}
{}
\end{entrylist}

\vspace{-0.8cm}
I have held a number of technology positions within BP, most recently CIO for analytics and data science; and before that head of technology strategy and head of technology innovation

\vspace{0.2cm} \emph{Illustrative achievements:}
\begin{itemize}
	\item Implementation of Cloudera CDH based Hadoop stack, design of stream based market data ingestion framework using Kafka.
	\item Managing a team of >80 people with global locations, including specialist Data Science, optimisation, and quant development teams.
	\item Delivery of multiple data science project across trading, and corporate functions including:
	\begin{itemize}
		\item Vessel destination and cargo prediction.
		\item Impact of weather on vessel ETA.
		\item Wind turbine misalignement modelling.
	\end{itemize}
	\item Creation of trading innovation function, and delivery of multiple short cycle prototypes covering topics from geospatial analytics, through twitter mining, to relationship and social interaction modelling.
	\item Creating an SoA architecture, strategy and subsequently overseeing the design and delivery of the technology implementation including designing the prototype for a Mobile Gateway.
	\item Insourcing of a delivery organisation, resulting in material (>20\%) savings and productivity improvements.
\end{itemize}


%------------------------------------------------
\begin{entrylist}
\entry
{2005--07}
{BP Plc - European Gas and Power Analytics}
{London, UK}
{}
\end{entrylist}

\vspace{-0.8cm}
Working in a hybrid commercial analytics / market risk role, supporting the trading business across all areas of risk management \& analytics.  

\vspace{0.2cm} \emph{Specific responsibilities of this role were:}
\begin{itemize}
	\item Design and implementation of a market risk system (which remained in operation for >10 years), including risk attribution, reporting and ‘what-if’ tooling.
	\item Day to day analytic tasks to generate trading insight, support market calls, or understand risk.
	\item Production of daily VaR numbers, documentation of drivers and presentation to traders and business unit management.
	\item Acting as subject matter expert to several strategic IT initiatives.
	\item Working as the liaison between the risk function and quantitative analysis teams.
\end{itemize}


%------------------------------------------------



%----------------------------------------------------------------------------------------
% INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} data analysis (including Kaggle / MooC), machine learning, data visualisation, big data analytics technologies, streamed data analytics, application of machine learning to trading, containerisation, micro-service design using python \\

\textbf{personal:} furniture making, Arduino hacking, running, cooking, spending time with my family (wife, daughter and dog)

%----------------------------------------------------------------------------------------
% PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

%\section{publications}
%
%\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography
%
%\printbibsection{book}{books} % Print all books from the bibliography
%
%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=bibheading]
%\end{refsection}
%
%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=bibheading]
%\end{refsection}
%
%\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography
%
%\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

\end{document}
